---
title: "extracting_fire_response_data"
author: "Sophie"
date: "25/08/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


# Start up AusTraits

Load packages and AusTraits

AusTraits can be accessed here:
https://zenodo.org/record/5112001

Or using the AusTraits package:
https://traitecoevo.github.io/austraits/

```{r}
library(tidyverse)

#austraits <- read_rds("raw_data/austraits-3.0.2.rds") # Latest release of austraits
austraits <- read_rds("raw_data/austraits-sophie-branch.rds") # This is an updated rds 
# file which includes the extra studies I added to austraits
```



---

# Extract fire_response trait records


Subset traits to fire_response records only

```{r}
fire_response <- 
  austraits$traits %>% 
  filter(trait_name == "fire_response") %>% 
  select(-trait_name) %>% 
  rename(fire_response = value)
```


Filter out non-native taxa

```{r}
aus_native_lookup <- read_csv("processed_data/aus_native_lookup.csv") 
# See "code/make_aus_native_species_list.R" for classifying natives and non-natives

fire_response <-
  fire_response %>% 
  left_join(aus_native_lookup,
            by = "taxon_name") %>% 
  filter(aus_native == TRUE) %>% 
  select(-aus_native)
```


Join taxonomic information 

```{r}
fire_response <-
    fire_response %>% 
    left_join(austraits$taxa %>% 
                select(taxon_name, genus, family, taxonRank, taxonomicStatus, taxonDistribution), 
              by = "taxon_name")
```


Filter to species level and below species level data

```{r}
fire_response_cleaned <-
  fire_response %>% 
  filter(taxonRank == "Forma" | 
         taxonRank == "Species" | 
         taxonRank == "Varietas" | 
         taxonRank == "Subspecies",
         taxonomicStatus == "accepted")
```


Create dataframe with tallies of the number of observations for each value

```{r}
fire_response_summary <- 
    fire_response_cleaned %>% 
    group_by(taxon_name, fire_response, taxonRank) %>%
    summarise(count = n()) %>% 
    pivot_wider(names_from = fire_response,
                values_from = count) %>% 
    ungroup() %>% 
    mutate(across(where(is.integer), ~ replace_na(., 0))) 

names(fire_response_summary) <- 
  names(fire_response_summary) %>% 
  str_replace_all(c(" " = "_"))
```


Calculate a binary column for whether there is variation in observations across AusTraits

```{r}
col <- colnames(fire_response_summary)
col <- col[!col %in% c("taxon_name", "taxonRank")]

fire_response_summary <-
  fire_response_summary %>% 
  mutate(variation_in_strat = (rowSums(fire_response_summary[,col] > 0) > 1))
```



Exclude taxa that are observed as fire_not_relevant or unknown

```{r}
fire_response_summary <-
  fire_response_summary %>% 
  filter(!(fire_not_relevant >= 1 | 
           fire_not_relevant_resprouts >= 1 | # Unsure if I should exclude
           fire_not_relevant_not_fire_killed_does_not_resprout >= 1 | # Unsure if I should exclude
           fire_killed_fire_not_relevant >= 1)) # Unsure if I should exclude
```


## For taxa with no variation in observation of fire response strategy

```{r}
fire_response_summary <- 
  fire_response_summary %>% 
  mutate(resprouting = if_else(variation_in_strat == FALSE,
                               case_when(fire_killed >= 1 ~ "does not resprout",
                                 resprouts >= 1 ~ "mostly resprouts",
                                 fire_killed_resprouts >= 1 ~ "sometimes resprouts",
                                 not_fire_killed_does_not_resprout >= 1 ~ "does not resprout"),
                               "NA"))
```


## For taxa with variation

Make columns that tally the number of observations of fire-killed, resprouts, mixed
fire responses, fire resistors and no fire exposure into two groups (resprouts or
does not resprout)

```{r}
fire_response_summary <-
  fire_response_summary %>% 
  mutate(resprout_tally = resprouts + fire_killed_resprouts,
         does_not_resprout_tally = fire_killed + fire_killed_resprouts + not_fire_killed_does_not_resprout)
```


Plot histogram of percentage of resprout observations

```{r}
fire_response_summary <-
    fire_response_summary %>% 
    mutate(resprout_percent = resprout_tally / (resprout_tally + does_not_resprout_tally))

fire_response_summary %>% 
    filter(variation_in_strat == TRUE) %>% 
    ggplot(aes(x = resprout_percent)) +
    geom_histogram() +
    scale_x_continuous(breaks = seq(0.0, 1.0, by = 0.1)) +
    theme_classic()

# Plot to decide where the cutoff is for species that do not resprout, 'sometimes'
# resprout and 'mostly' resprouts -> If over 60% of observations are tallied for resprouting
# the species 'mostly resprouts'
```


If over 60% of observations are resprouts, then can designate as mostly resprouts.
If no observations are resprouts, designate as does not resprout.
If less than 60% but more than 0 observations are resprouts, then designate as sometimes
resprouts.

```{r}
fire_response_summary <- 
  fire_response_summary %>% 
  mutate(resprouting = if_else(variation_in_strat == TRUE,
                                  case_when(
                                    resprout_tally == 0 ~ 
                                      "does not resprout", 
                                    (resprout_tally / (resprout_tally + does_not_resprout_tally) < 0.6) ~
                                      "sometimes resprouts",
                                    (resprout_tally / (resprout_tally + does_not_resprout_tally) >= 0.6) ~ 
                                      "mostly resprouts"),
                                  resprouting))
```



Summary of final resprouting values and counts

```{r}
fire_response_summary %>% 
    group_by(resprouting) %>% 
    summarise(count = n()) %>% 
    ungroup()

# Final tibble for resprouting variable
resprouting <- 
    fire_response_summary %>% 
    select(taxon_name, taxonRank, resprouting)
```


---

# Extract fire_cued_seeding trait records


Subset traits to fire_cued_seeding records only

```{r}
fire_cued_seeding <- 
  austraits$traits %>% 
  filter(trait_name == "fire_cued_seeding") %>% 
  select(-trait_name) %>% 
  rename(fire_cued_seeding = value)
```


Filter out non-native species

```{r}
fire_cued_seeding <-
  fire_cued_seeding %>% 
  left_join(aus_native_lookup,
            by = "taxon_name") %>% 
  filter(aus_native == TRUE) %>% 
  select(-aus_native)
```


Join taxonomic information 

```{r}
fire_cued_seeding <-
    fire_cued_seeding %>% 
    left_join(austraits$taxa %>% 
                select(taxon_name, genus, family, taxonRank, taxonomicStatus, taxonDistribution), 
              by = "taxon_name")
```


Filter to species level and below species level data

```{r}
fire_cued_seeding_cleaned <-
  fire_cued_seeding %>% 
  filter(taxonRank == "Forma" | 
         taxonRank == "Species" | 
         taxonRank == "Varietas" | 
         taxonRank == "Subspecies",
         taxonomicStatus == "accepted")
```



Create dataframe with tallies of the number of observations for each value

```{r}
fire_cued_seeding_summary <- 
    fire_cued_seeding_cleaned %>% 
    group_by(taxon_name, fire_cued_seeding, taxonRank) %>%
    summarise(count = n()) %>% 
    pivot_wider(names_from = fire_cued_seeding,
                values_from = count) %>% 
    ungroup() %>% 
    mutate(across(where(is.integer), ~ replace_na(., 0))) 

names(fire_cued_seeding_summary) <- 
  names(fire_cued_seeding_summary) %>% 
  str_replace_all(c(" " = "_"))
```


Calculate a binary column for whether there is variation in observations

```{r}
col <- colnames(fire_cued_seeding_summary)
col <- col[!col %in% c("taxon_name", "taxonRank")]

fire_cued_seeding_summary <-
  fire_cued_seeding_summary %>% 
  mutate(variation_in_seeding = (rowSums(fire_cued_seeding_summary[,col] > 0) > 1)) 
```


## For taxa with no variation in observation of fire-cued seeding 

```{r}
fire_cued_seeding_summary <- 
  fire_cued_seeding_summary %>% 
  mutate(post_fire_seeding = if_else(variation_in_seeding == FALSE,
                                     case_when(fire_cued_seeding >= 1 ~ 
                                                 "robust post-fire seeding",
                                               no_fire_cued_seeding >= 1 ~ 
                                                 "no post-fire seeding",
                                               fire_cued_seeding_incomplete_germination >= 1 ~ 
                                                 "some post-fire seeding",
                                               fire_cued_seeding_high_fire_cued_seeding_moderate >= 1 ~ 
                                                 "robust post-fire seeding",
                                               fire_cued_seeding_high >= 1 ~
                                                 "robust post-fire seeding",
                                               fire_cued_seeding_minimal >= 1 ~
                                                 "some post-fire seeding",
                                               fire_cued_seeding_complete_germination >= 1 ~
                                                 "robust post-fire seeding",
                                               fire_cued_seeding_minimal_no_fire_cued_seeding >= 1 ~
                                                 "some post-fire seeding",
                                               fire_cued_seeding_no_fire_cued_seeding >= 1 ~
                                                 "some post-fire seeding",
                                               fire_cued_seeding_moderate >= 1 ~
                                                 "robust post-fire seeding", 
                                              fire_cued_seeding_high_fire_cued_seeding_minimal_no_fire_cued_seeding >= 1 ~
                                                 "some post-fire seeding",
                                               fire_cued_seeding_moderate_no_fire_cued_seeding >= 1 ~
                                                 "some post-fire seeding"),
                                     "NA"))
```



## For taxa with no variation


Make columns that tally the number of observations into two groups - fire-cued seeding
or no fire-cued seeding

```{r}
fire_cued_seeding_summary <-
  fire_cued_seeding_summary %>% 
  mutate(fire_cued_seeding_tally = 
           fire_cued_seeding + 
           fire_cued_seeding_incomplete_germination +
           fire_cued_seeding_high_fire_cued_seeding_moderate + 
           fire_cued_seeding_high +
           fire_cued_seeding_complete_germination + 
           fire_cued_seeding_high_no_fire_cued_seeding +
           fire_cued_seeding_no_fire_cued_seeding + 
           fire_cued_seeding_moderate + 
           fire_cued_seeding_high_fire_cued_seeding_minimal + 
           fire_cued_seeding_minimal_fire_cued_seeding_moderate + 
           fire_cued_seeding_high_fire_cued_seeding_minimal_no_fire_cued_seeding +
           fire_cued_seeding_moderate_no_fire_cued_seeding,
         no_seeding_tally = 
           no_fire_cued_seeding + 
           fire_cued_seeding_minimal +  
           fire_cued_seeding_high_no_fire_cued_seeding +
           fire_cued_seeding_minimal_no_fire_cued_seeding + 
           fire_cued_seeding_no_fire_cued_seeding +
           fire_cued_seeding_high_fire_cued_seeding_minimal + 
           fire_cued_seeding_minimal_fire_cued_seeding_moderate +
           fire_cued_seeding_high_fire_cued_seeding_minimal_no_fire_cued_seeding +
           fire_cued_seeding_moderate_no_fire_cued_seeding)
```


Plot histogram of percentage of seeding observations

```{r}
fire_cued_seeding_summary <-
  fire_cued_seeding_summary %>% 
  mutate(seeding_percent = fire_cued_seeding_tally / (fire_cued_seeding_tally + no_seeding_tally))

fire_cued_seeding_summary %>% 
  filter(variation_in_seeding == TRUE) %>% 
  ggplot(aes(x = seeding_percent)) +
  geom_histogram() +
  scale_x_continuous(breaks = seq(0.0, 1.0, by = 0.1)) +
  theme_bw()
```


If over 60% of observations are fire-cued seeding, then can designate as robust 
post-fire seeding. If no observations are fire-cued seeding, designate as no post-fire
seeding. If less than 60% but more than 0 observations are fire-cued seeding, then 
designate as some post-fire seeding. (Decided 60% based on previous histogram)

```{r}
fire_cued_seeding_summary <- 
  fire_cued_seeding_summary %>% 
  mutate(post_fire_seeding = if_else(variation_in_seeding == TRUE,
                                  case_when(
                                    fire_cued_seeding_tally == 0 ~ 
                                      "no post-fire seeding", 
                                    (fire_cued_seeding_tally / (fire_cued_seeding_tally + no_seeding_tally) < 0.6) ~
                                      "some post-fire seeding",
                                    (fire_cued_seeding_tally / (fire_cued_seeding_tally + no_seeding_tally) >= 0.6) ~ 
                                      "robust post-fire seeding"),
                                  post_fire_seeding))
```


Summary of final seeding values and counts

```{r}
fire_cued_seeding_summary %>% 
  group_by(post_fire_seeding) %>% 
  summarise(count = n()) %>% 
  ungroup()

# Final tibble for seeding variable
post_fire_seeding <- fire_cued_seeding_summary %>% 
  select(taxon_name, taxonRank, post_fire_seeding)
```



---

# Join fire_response and fire_cued_seeding

```{r}
fire_response_taxa <- fire_response_summary$taxon_name %>% unique() # 8220 taxa
seeding_taxa <- fire_cued_seeding_summary$taxon_name %>% unique() # 3013 taxa

intersecting_taxa <- intersect(fire_response_taxa, seeding_taxa)
# 2935 taxa intersect between fire_cued_seeding and fire_response
```


Join resprouting and seeding variables

```{r}
resprouting_seeding <- 
  resprouting %>% 
  full_join(post_fire_seeding, by = c("taxon_name", "taxonRank"))

resprouting_seeding <-
  resprouting_seeding %>% 
  mutate(data_on_both = !is.na(resprouting) & !is.na(post_fire_seeding))
```


Make new resprouter or seeder variable

```{r}
resprouting_seeding <-
  resprouting_seeding %>% 
  mutate(resprouter_or_seeder = case_when(
    (resprouting == "mostly resprouts" | resprouting == "sometimes resprouts") & (post_fire_seeding == "no post-fire seeding" | is.na(post_fire_seeding)) ~ 
      "resprouter",
    (post_fire_seeding == "some post-fire seeding" | post_fire_seeding == "robust post-fire seeding") & (resprouting == "does not resprout" | is.na(resprouting)) ~ 
      "seeder",
    (resprouting == "mostly resprouts" | resprouting == "sometimes resprouts") & (post_fire_seeding == "some post-fire seeding" | post_fire_seeding == "robust post-fire seeding") ~ 
      "facultative",
    (resprouting == "does not resprout" | is.na(resprouting)) & (post_fire_seeding == "no post-fire seeding" | is.na(post_fire_seeding)) ~
      "neither"))
```


Clean data

```{r}
# Remove hybrids
resprouting_seeding <-
  resprouting_seeding %>% 
  filter(!str_detect(taxon_name, 
                     pattern = " x "))

# Align taxonRank values with gbif taxonrank values
resprouting_seeding$taxonRank <-
  resprouting_seeding$taxonRank %>% 
  str_replace("Forma", "Form") 

resprouting_seeding$taxonRank <-
  resprouting_seeding$taxonRank %>% 
  str_replace("Varietas", "Variety") 

resprouting_seeding$taxonRank <-
  resprouting_seeding$taxonRank %>% 
  toupper()

# Make variables ordered factors
resprouting_seeding$resprouting <- 
  factor(resprouting_seeding$resprouting, 
         ordered = TRUE,
         levels = c("does not resprout", "sometimes resprouts", "mostly resprouts"))

resprouting_seeding$post_fire_seeding <- 
  factor(resprouting_seeding$post_fire_seeding, 
         ordered = TRUE,
         levels = c("no post-fire seeding", "some post-fire seeding", "robust post-fire seeding"))

resprouting_seeding$resprouter_or_seeder <- 
  factor(resprouting_seeding$resprouter_or_seeder, 
         ordered = TRUE,
         levels = c("resprouter", "seeder", "facultative", "neither"))
```


Summarise values

```{r}
resprouting_seeding %>% 
  group_by(resprouter_or_seeder) %>% 
  summarise(count = n()) %>% 
  ungroup()

# Filter for taxa with data on both variables
resprouting_seeding %>% 
  filter(data_on_both == TRUE) %>% 
  group_by(resprouter_or_seeder) %>% 
  summarise(count = n()) %>% 
  ungroup()
```



---

Add in growth form column

```{r}
growth_forms <-
  austraits$traits %>% 
  filter(trait_name == "plant_growth_form") %>% 
  select(taxon_name, value) %>% 
  rename(growth_form = value)

resprouting_seeding_gf <-
  resprouting_seeding %>% 
  left_join(growth_forms, by = "taxon_name") %>% 
  group_by(taxon_name, taxonRank, resprouting, 
           post_fire_seeding, data_on_both, resprouter_or_seeder) %>% 
  summarise(final_growth_form = names(sort(table(growth_form, useNA = "ifany"), decreasing = TRUE)[1])) %>% 
  ungroup()
```



Column for woody or herbaceous

```{r}
# Put semi-woody plants like tree ferns, palms and cycads as ambiguous
ambiguous <- 
    c("climber", "climber_herb climber_shrub", "climber_scrambler", "climber_twiner", 
      "climber_vine", "epiphyte", "geophyte", "hemi-parasite parasite", "parasite", 
      "prostrate", NA)
woody <- 
    c("climber_liana", "climber_shrub", "prostrate_shrub", "shrub", "shrub tree", 
      "shrub treelet", "subshrub", "tree", "treelet")
herbaceous <- 
    c("aquatic", "aquatic_herb", "climber_herb", "climber_vine_herbaceous", "fern", 
      "graminoid", "graminoid_not_tussock", "graminoid_not_tussock_tall", "graminoid_tussock",
      "graminoid_tussock_tall", "herb", "herb_large", "prostrate_herb", "short_basal", 
      "long_basal", "erect_leafy", "herb shrub")
semi_woody <- 
    c("cycad", "fern_tree", "palm", "pandanus")
```



```{r}
resprouting_seeding_gf <-
    resprouting_seeding_gf %>% 
    mutate(woody_or_herb = case_when(final_growth_form %in% woody ~ "woody",
                                     final_growth_form %in% herbaceous ~ "herb",
                                     final_growth_form %in% semi_woody ~ "semi-woody",
                                     final_growth_form %in% ambiguous ~ "unclear"))

resprouting_seeding_gf %>% 
    group_by(woody_or_herb) %>% 
    summarise(count = n()) %>% 
    ungroup()

# 3003 herbs, 4825 woody, 12 semi-woody, 422 unclear
```


Make binomial fire response variables

```{r}
resprouting_seeding <-
    resprouting_seeding_gf %>% 
    mutate(resprouting_binomial = case_when(
               resprouting %in% c("mostly resprouts", "sometimes resprouts") ~ TRUE, 
               resprouting %in% c("does not resprout") ~ FALSE),
           seeding_binomial = case_when(
               post_fire_seeding %in% c("robust post-fire seeding", "some post-fire seeding") ~ TRUE,
               post_fire_seeding %in% c("no post-fire seeding") ~ FALSE),
           obligate_resprouting_or_seeding = if_else(data_on_both == TRUE, case_when(
               resprouter_or_seeder == "seeder" ~ "obligate seeder",
               resprouter_or_seeder == "resprouter" ~ "obligate resprouter"
           ), NA_character_),
           resprouting_seeding_binomial = if_else(data_on_both == TRUE, case_when(
             resprouting == "mostly resprouts" & post_fire_seeding == "some post-fire seeding" ~ "resprouter",
             resprouting == "sometimes resprouts" & post_fire_seeding == "robust post-fire seeding" ~ "seeder",
             resprouter_or_seeder == "seeder" ~ "seeder",
             resprouter_or_seeder == "resprouter" ~ "resprouter"
           ), NA_character_))
```



Make ordered factors
```{r}
resprouting_seeding$resprouting <- 
  factor(resprouting_seeding$resprouting, 
         ordered = TRUE,
         levels = c("does not resprout", "sometimes resprouts", "mostly resprouts"))

resprouting_seeding$post_fire_seeding <- 
  factor(resprouting_seeding$post_fire_seeding, 
         ordered = TRUE,
         levels = c("no post-fire seeding", "some post-fire seeding", "robust post-fire seeding"))

resprouting_seeding$resprouter_or_seeder <- 
  factor(resprouting_seeding$resprouter_or_seeder, 
         ordered = TRUE,
         levels = c("resprouter", "seeder", "facultative", "neither"))

saveRDS(resprouting_seeding, "processed_data/resprouting_seeding.rds")
```


---

# Read in gbif data

The GBIF download and cleaning process is in "code/gbif_cleaning_process.R"

The doi for our GBIF download is: https://doi.org/10.15468/dl.6rghq7

```{r}
gbif <- read_csv("raw_data/filt_aus_limited_columns_v3.csv") %>% select(-day, -month, -year)
```


Add in matching taxa with manually found taxonomic synonyms

```{r}
# Read in new csv with manually found taxonomic synonyms
non_matching_taxa_matched <- read_csv("processed_data/non_matching_taxa_matched.csv")
```


Add column with the gbif names that can be matched to austraits

```{r}
# Replace austraits taxa with manually matched synonyms
resprouting_seeding <-
  resprouting_seeding %>% 
  left_join(non_matching_taxa_matched,
            by = c("taxon_name" = "non_matching_taxa")) %>% 
  select(-no_occurrences)

resprouting_seeding <-
  resprouting_seeding %>% 
  mutate(taxon_name = if_else(
    !is.na(matched_with_gbif),
    matched_with_gbif,
    taxon_name
  )) %>% 
  select(-matched_with_gbif)


# Mutate gbif taxa to be the same names in austraits

gbif <-
  gbif %>% 
  mutate(matched_name = case_when(scientificname %in% resprouting_seeding$taxon_name ~
                                    scientificname,
                                  verbatimscientificname %in% resprouting_seeding$taxon_name ~
                                    verbatimscientificname,
                                  species %in% resprouting_seeding$taxon_name ~
                                    species))
```


## Join gbif species occurrences to austraits data


```{r}
joined_fire_data_inner <-
  resprouting_seeding %>% 
  inner_join(gbif, by = c("taxon_name" = "matched_name", "taxonRank" = "taxonrank"))

joined_fire_data_inner_taxa <- joined_fire_data_inner$taxon_name %>% unique()
```


```{r}
# Non-matching taxa
joined_fire_data_anti <-
  resprouting_seeding %>% 
  anti_join(gbif, by = c("taxon_name" = "matched_name", "taxonRank" = "taxonrank"))

#joined_fire_data_anti <-
#  joined_fire_data_anti %>% 
#  mutate(matched_with_gbif = NA)

#write_csv(joined_fire_data_anti, "processed_data/non_matching_taxa.csv")

# These are probably rare species or the names are not accepted in WCVP
```



## Try use Will's powo_apc_lookup to match more taxa

```{r}
powo_apc_lookup <- read_csv("processed_data/powo_apc_lookup.csv")
# See "code/make_taxonomy_lookup.R" for making matches between POWO/WCVP/GBIF and
# AusTraits (APC)
```


```{r}
resprouting_seeding <-
    resprouting_seeding %>%
    mutate(binomialAPCname = word(taxon_name, 1, 2)) 

resprouting_seeding <-
    resprouting_seeding %>% 
    left_join(powo_apc_lookup, by = c("binomialAPCname", "taxonRank"))

manual_matches <- c("Boronia anemonifolia", 
                    "Cuscuta australis",
                    "Cyperus pygmaeus",
                    "Grewia latifolia",
                    "Heliotropium paniculatum",
                    "Hibiscus pentaphyllus",
                    "Leucopogon cuspidatus",
                    "Trichocline spathulata")

# Only picked the ones where it was unambiguous what the matching GBIF name is
# E.g. if a taxa could be matched to multiple different GBIF taxa then I did not
# swap it
# Since all the taxa I found were species level, I could just match to the binomial
# POWO name

# Replace austraits taxa with GBIF names
resprouting_seeding <-
    resprouting_seeding %>% 
    mutate(taxon_name = if_else(taxon_name %in% manual_matches, 
                                binomialPOWOname, # Replace with POWO name
                                taxon_name)) # Else, leave it

resprouting_seeding <-
    resprouting_seeding %>% 
    select(-fullAPCname, -binomialAPCname, -binomialPOWOname, -POWOinfra) %>% 
    distinct(.keep_all = TRUE)

# Mutate gbif taxa to be the same names in austraits
gbif <-
  gbif %>% 
  mutate(matched_name = case_when(scientificname %in% resprouting_seeding$taxon_name ~
                                    scientificname,
                                  verbatimscientificname %in% resprouting_seeding$taxon_name ~
                                    verbatimscientificname,
                                  species %in% resprouting_seeding$taxon_name ~
                                    species))

# Does not include austraits taxa that cannot be matched to gbif records
joined_fire_data_inner <-
    resprouting_seeding %>% 
    inner_join(gbif, by = c("taxon_name" = "matched_name", "taxonRank" = "taxonrank"))

joined_fire_data_inner_taxa <- joined_fire_data_inner$taxon_name %>% unique()

saveRDS(joined_fire_data_inner, file = "processed_data/fire_response_and_gbif_data.rds")
```



