---
title: "fire_response_strategies_and_leaf_traits"
author: "Sophie"
date: "11/01/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---


AusTraits can be accessed here:
https://zenodo.org/record/5112001

Or using the AusTraits package:
https://traitecoevo.github.io/austraits/

```{r}
library(tidyverse)
library(grid)
library(RColorBrewer)
library(phylolm)
austraits <- read_rds("raw_data/austraits-sophie-branch.rds") # This is an updated 
# rds file which includes the extra studies I added to austraits
```


Read in SLA and leaf N data

```{r}
sla <- 
  austraits$traits %>% 
  filter(trait_name == "specific_leaf_area") %>% 
  select(-trait_name) %>% 
  rename(specific_leaf_area = value)

sla$specific_leaf_area <- as.numeric(sla$specific_leaf_area)

leaf_n <- 
  austraits$traits %>% 
  filter(trait_name == "leaf_N_per_dry_mass") %>% 
  select(-trait_name) %>% 
  rename(leaf_N_per_dry_mass = value)

leaf_n$leaf_N_per_dry_mass <- as.numeric(leaf_n$leaf_N_per_dry_mass)
```


Calculate mean SLA and leaf N for each taxa

```{r}
mean_sla <- 
    sla %>% 
    group_by(taxon_name) %>% 
    summarise(mean_sla = mean(specific_leaf_area)) %>% 
    ungroup()

mean_leaf_n <- 
    leaf_n %>% 
    group_by(taxon_name) %>% 
    summarise(mean_leaf_n = mean(leaf_N_per_dry_mass)) %>% 
    ungroup()
```


Join to fire response 

```{r}
fire_response_and_mean_fris <- read_csv("processed_data/final_df_predicted_fris_and_fire_response.csv")
# Produced from "code/fire_response_strategies_and_fire_frequency.Rmd"

fire_response_and_leaf_traits <- 
    fire_response_and_mean_fris %>% 
    left_join(mean_sla) %>% 
    left_join(mean_leaf_n)
```



# Run linear models

```{r}
library(emmeans)

leaf_traits_woody_herb_only <- fire_response_and_leaf_traits %>% 
    filter(woody_or_herb %in% c("woody", "herb"))
leaf_traits_woody_herb_only$woody_or_herb <- 
    leaf_traits_woody_herb_only$woody_or_herb %>%  
    factor(ordered = TRUE, levels = c("woody", "herb"))


facet_labels <- c("woody" = "Woody",
                  "herb" = "Herbaceous")

m1 <- lm(mean_sla ~ resprouting_binomial * woody_or_herb, data = leaf_traits_woody_herb_only)
summary(m1)

emm1 <- emmeans(m1, specs = pairwise ~ resprouting_binomial:woody_or_herb)
emm1$contrasts %>% confint()

annotations_p1 <- data.frame(label = c("p = <0.0001", ""), woody_or_herb = c("herb", "woody"))
annotations_p1$woody_or_herb <- annotations_p1$woody_or_herb %>% factor(ordered = TRUE, levels = c("woody", "herb"))

p1 <-
    leaf_traits_woody_herb_only %>% 
    drop_na(resprouting_binomial) %>% 
    ggplot(aes(x = resprouting_binomial, y = mean_sla, fill = woody_or_herb)) +
    geom_violin(size = 0.8) +
    geom_boxplot(width = 0.05, size = 0.8) +
#    geom_text(aes(x = 2.1, y = 0.1, label = label), data = annotations_p1,
#              size = 4, fontface = "bold") +
    facet_wrap(~woody_or_herb,
               labeller = as_labeller(facet_labels)) +
    scale_y_log10() +
    labs(x = "Resprouting", y = bquote("SLA (" *mm^2/mg *")")) +
    scale_fill_manual(values = c("#915330", "#aedb65"),
                      name = "", 
                      breaks = c("woody", "herb"),
                      labels = c("Woody", "Herb")) +
    theme_classic() +
    theme(panel.background = element_rect(colour = "black", fill = NA, size = 0.5),
          plot.margin = unit(c(0.1,1,0.05,0.1), "cm"),
          axis.text.y = element_text(colour = "black", size = 10),
          axis.title.y = element_text(size = 12, margin = margin(0,1,0,0)),
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          legend.position = "none",
          strip.background = element_rect(colour = "black", size = 0.5, fill = "#f0f0f0"),
          strip.text = element_text(size = 11, face = "bold"),
          panel.spacing = unit(0.2, "cm"),
          axis.line = element_blank()) 
p1
```


Rerun with phylogenetic linear model (some taxa are dropped because cannot be matched
to a tip on the phylogeny)

```{r}
tree <- read.tree("raw_data/v0.1-big-seed-plant-trees/ALLMB.tre")

# Phylogeny tree is available here:
# https://github.com/FePhyFoFum/big_seed_plant_trees
# Smith SA, Brown JW. 2018. Constructing a broadly inclusive seed plant phylogeny. American Journal of Botany 105: 302–314.

leaf_traits_woody_herb_only$taxon_name <- gsub(" ", "_", leaf_traits_woody_herb_only$taxon_name)
leaf_traits_woody_herb_only <- leaf_traits_woody_herb_only[leaf_traits_woody_herb_only$taxon_name %in% tree$tip.label,]
leaf_traits_woody_herb_only$resprouting_binomial <- 
    ifelse(leaf_traits_woody_herb_only$resprouting_binomial == TRUE, 1, 0) # Make numeric

pruned_tree <- drop.tip(tree, setdiff(tree$tip.label, leaf_traits_woody_herb_only$taxon_name))
pruned_tree <- as.phylo(pruned_tree)

sorted_data <- leaf_traits_woody_herb_only[order(match(leaf_traits_woody_herb_only$taxon_name, pruned_tree$tip.label)),]

sorted_data <-
    sorted_data %>%
    select(taxon_name, mean_sla, mean_leaf_n, resprouting_binomial, seeding_binomial, woody_or_herb) %>% 
    column_to_rownames("taxon_name")


# Return old variable to original state for running normal lm's 
leaf_traits_woody_herb_only <- fire_response_and_leaf_traits %>% 
    filter(woody_or_herb %in% c("woody", "herb"))
leaf_traits_woody_herb_only$woody_or_herb <- 
    leaf_traits_woody_herb_only$woody_or_herb %>%  
    factor(ordered = TRUE, levels = c("woody", "herb"))

pm1 <-
    phylolm(mean_sla ~ resprouting_binomial * woody_or_herb, 
            data = sorted_data,
            phy = pruned_tree, 
            model = "BM")
summary(pm1)
```



```{r}
m2 <- lm(mean_leaf_n ~ resprouting_binomial * woody_or_herb, data = leaf_traits_woody_herb_only)
summary(m2)

emm2 <- emmeans(m2, specs = pairwise ~ resprouting_binomial:woody_or_herb)
emm2$contrasts %>% confint()

p2 <-
    leaf_traits_woody_herb_only %>% 
    drop_na(resprouting_binomial) %>% 
    ggplot(aes(x = resprouting_binomial, y = mean_leaf_n, fill = woody_or_herb)) +
    geom_violin(size = 0.8) +
    geom_boxplot(width = 0.05, size = 0.8) +
    facet_wrap(~woody_or_herb,
               labeller = as_labeller(facet_labels)) +
    scale_y_log10() +
    scale_x_discrete(labels = c("Non-\nresprouters", "Resprouters")) +
    scale_fill_manual(values = c("#915330", "#aedb65"),
                        name = "", 
                        breaks = c("woody", "herb"),
                        labels = c("Woody", "Herb")) +
    labs(x = "Resprouting", y = "Leaf N (mg/g)") +
    theme_classic() +
    theme(panel.background = element_rect(colour = "black", fill = NA, size = 0.5),
          plot.margin = unit(c(0.1,1,0.1,0.1), "cm"),
          axis.text = element_text(colour = "black", size = 10),
          axis.title.y = element_text(size = 12, margin = margin(0,1,0,0)),
          axis.title.x = element_text(size = 12, margin = margin(10,0,0,0), face = "bold"),
          legend.position = "none",
          strip.background = element_rect(colour = "black", size = 0.5, fill = "#f0f0f0"),
          strip.text = element_text(size = 11, face = "bold"),
          panel.spacing = unit(0.2, "cm"),
          axis.line = element_blank())
p2
```


Rerun with phylogenetic linear model

```{r}
pm2 <-
    phylolm(mean_leaf_n ~ resprouting_binomial * woody_or_herb, 
            data = sorted_data,
            phy = pruned_tree, 
            model = "BM")
summary(pm2)
```


```{r}
m3 <- lm(mean_sla ~ seeding_binomial * woody_or_herb, data = leaf_traits_woody_herb_only)
summary(m3)

emm3 <- emmeans(m3, specs = pairwise ~ seeding_binomial:woody_or_herb)
emm3$contrasts %>% confint()


annotations_p3 <- data.frame(label = c("p = 0.037", "p = <0.0001"), woody_or_herb = c("herb", "woody"))
annotations_p3$woody_or_herb <- annotations_p3$woody_or_herb %>% factor(ordered = TRUE, levels = c("woody", "herb"))

p3 <-
    leaf_traits_woody_herb_only %>% 
    drop_na(seeding_binomial) %>% 
    ggplot(aes(x = seeding_binomial, y = mean_sla, fill = woody_or_herb)) +
    geom_violin(size = 0.8) +
    geom_boxplot(width = 0.05, size = 0.8) +
#    geom_text(aes(x = 2.1, y = 0.1, label = label), data = annotations_p3,
#              size = 4, fontface = "bold") +
    facet_wrap(~woody_or_herb,
               labeller = as_labeller(facet_labels)) +
    scale_y_log10() +
    scale_fill_manual(values = c("#915330", "#aedb65"),
                        name = "", 
                        breaks = c("woody", "herb"),
                        labels = c("Woody", "Herb")) +
    labs(x = "Post-fire Seeding", y = bquote("SLA (" *mm^2/mg *")")) +
    theme_classic() +
    theme(panel.background = element_rect(colour = "black", fill = NA, size = 0.5),
          plot.margin = unit(c(0.1,0.1,0.05,0.1), "cm"),
          axis.ticks.y = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.text = element_text(colour = "black", size = 10),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          legend.position = "none",
          strip.background = element_rect(colour = "black", size = 0.5, fill = "#f0f0f0"),
          strip.text = element_text(size = 11, face = "bold"),
          panel.spacing = unit(0.2, "cm"),
          axis.line = element_blank())
p3
```

Rerun with phylogenetic linear model

```{r}
pm3 <-
    phylolm(mean_sla ~ seeding_binomial * woody_or_herb, 
            data = sorted_data,
            phy = pruned_tree, 
            model = "BM")
summary(pm3)
```


```{r}
m4 <- lm(mean_leaf_n ~ seeding_binomial * woody_or_herb, data = leaf_traits_woody_herb_only)
summary(m4)

emm4 <- emmeans(m4, specs = pairwise ~ seeding_binomial:woody_or_herb)
emm4$contrasts %>% confint()


annotations_p4 <- data.frame(label = c("p = 0.050", ""), woody_or_herb = c("herb", "woody"))
annotations_p4$woody_or_herb <- annotations_p4$woody_or_herb %>% factor(ordered = TRUE, levels = c("woody", "herb"))

p4 <-
    leaf_traits_woody_herb_only %>% 
    drop_na(seeding_binomial) %>% 
    ggplot(aes(x = seeding_binomial, y = mean_leaf_n, fill = woody_or_herb)) +
    geom_violin(size = 0.8) +
    geom_boxplot(width = 0.05, size = 0.8) +
#    geom_text(aes(x = 2.1, y = 2.1, label = label), data = annotations_p4,
#              size = 4, fontface = "bold") +
    facet_wrap(~woody_or_herb,
               labeller = as_labeller(facet_labels)) +
    scale_x_discrete(labels = c("Non-seeders", "Seeders")) +
    scale_y_log10() +
    scale_fill_manual(values = c("#915330", "#aedb65"),
                        name = "", 
                        breaks = c("woody", "herb"),
                        labels = c("Woody", "Herb")) +
    labs(x = "Post-fire Seeding", y = "Leaf N (mg/g)") +
    theme_classic() +
    theme(panel.background = element_rect(colour = "black", fill = NA, size = 0.5),
          plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm"),
          axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.text = element_text(colour = "black", size = 10),
          axis.title.y = element_blank(),
          axis.title.x = element_text(size = 12, margin = margin(10,0,0,0), face = "bold"),
          legend.position = "none",
          strip.background = element_rect(colour = "black", size = 0.5, fill = "#f0f0f0"),
          strip.text = element_text(size = 11, face = "bold"),
          panel.spacing = unit(0.2, "cm"),
          axis.line = element_blank())
p4
```

Rerun with phylogenetic linear model

```{r}
pm4 <-
    phylolm(mean_leaf_n ~ seeding_binomial * woody_or_herb, 
            data = sorted_data,
            phy = pruned_tree, 
            model = "BM")
summary(pm4)
```


```{r}
grid.draw(rbind(cbind(ggplotGrob(p1), ggplotGrob(p3)), cbind(ggplotGrob(p2), ggplotGrob(p4))))

final_plot <- rbind(cbind(ggplotGrob(p1), ggplotGrob(p3)), cbind(ggplotGrob(p2), ggplotGrob(p4)))
#ggsave("leaf_traits.png", plot = final_plot, width = 8.5, height = 4.8)
```




