---
title: "fire_response_strategy_and_fire_frequency"
author: "Sophie"
date: "22/11/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


Load libraries

```{r}
library(tidyverse)
```
 

Read in fire response strategy data

```{r}
resprouting_seeding_binomial <- readRDS("processed_data/resprouting_seeding.rds")
# R object produced by "code/extracting_fire_response_data.Rmd"
```


---

# FRI data from Poisson Regression method


Read in mean fire return interval data

```{r}
mean_fris <- read_csv("processed_data/mean_fris_from_poisson_method.csv", guess_max = 8009)
# csv file produced from "code/mean_fri_poisson_regression_method.Rmd"

mean_fris <-
    mean_fris %>% 
    left_join(resprouting_seeding_binomial, by = c("taxon_name"))
```


Filter out taxa with warning messages

```{r}
mean_fris_no_errors <- 
    mean_fris %>% 
    filter(is.na(warnings), is.na(error), is.na(messages)) %>%
    select(-warnings, -messages, -error)
```


```{r}
write_csv(mean_fris_no_errors, "processed_data/final_df_predicted_fris_and_fire_response.csv")
```


Histogram of mean FRIs

```{r}
hist(mean_fris_no_errors$mean_fri) 
```


---

# Binomial logistic regression


## Resprouting binomial

Clean mean FRI data

```{r}
mean_fris_no_errors <- read_csv("processed_data/final_df_predicted_fris_and_fire_response.csv")

mean_fris_clean <-
    mean_fris_no_errors %>% 
    filter(upr_confint > 0)
```



```{r}
library(ggeffects)
library(RColorBrewer)
library(sjPlot)

df_woody_herb_only <- 
    mean_fris_clean %>%
    filter(woody_or_herb %in% c("woody", "herb")) 

df_woody_herb_only$resprouting_binomial <- 
    df_woody_herb_only$resprouting_binomial %>% as.factor()

m1 <- glm(resprouting_binomial ~ log10(mean_fri) + I(log10(mean_fri)^2) + log10(mean_fri):woody_or_herb + I(log10(mean_fri)^2):woody_or_herb + woody_or_herb,
          data = df_woody_herb_only,
          family = binomial)

summary(m1)

ggpredict(m1, c("mean_fri", "woody_or_herb")) %>% 
    ggplot(aes(x, predicted, color = group)) +
    geom_line(size = 1) +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.2, linetype = 0) +
    scale_x_log10() +
    ylab("Resprouting Probability") +
    xlab("Mean FRI") +
    theme_classic()

tab_model(m1)
```


Plot resprouting probability against fire frequency

```{r}
coef2 <- coef(m1)
x1 <- log10(df_woody_herb_only$mean_fri)
x2 <- df_woody_herb_only$woody_or_herb
x2 <- ifelse(x2 == "woody", 1, 0)
pred_y <- coef2[1] + coef2[2]*x1 + coef2[3]*x1^2 + coef2[4]*x2 + coef2[5]*x1*x2 + coef2[6]*x1^2*x2
pred_p <- exp(pred_y) / (1 + exp(pred_y))
df1 <- data.frame(x1, x2, df_woody_herb_only$woody_or_herb, pred_y, pred_p)
df1 <- df1 %>% rename(woody_or_herb = df_woody_herb_only.woody_or_herb)


p1 <-
    ggplot(data = df1, aes(x = 10^x1, y = pred_p, col = woody_or_herb)) +
    geom_line(size = 1.3) +
    scale_x_log10(expand = c(0,0),
                  limits = c(1.05,5000),
                  breaks = c(10,100,1000),
                  labels = c(10,100,1000)) +
    scale_y_continuous(limits = c(0,0.8),
                       expand = c(0,0)) +
    ylab("Resprouting Probability") +
    xlab("Fire Return Interval (Years)") +
    scale_colour_manual(values = c("#915330", "#aedb65"),
                        name = "", 
                        breaks = c("woody", "herb"),
                        labels = c("Woody", "Herb")) +
    ggtitle("a)") +
    theme_classic() +
    theme(panel.border = element_rect(colour = "black", fill = NA),
          legend.position = "none",
          axis.text = element_text(colour = "black", size = 8),
          plot.margin = unit(c(0.1,0.5,0.1,0.1), "cm"),
          plot.title.position = "plot",
          plot.title = element_text(size = 13, margin = margin(0,0,10,0)),
          axis.title.y = element_text(size = 10, margin = margin(0,8,0,0)),
          axis.title.x = element_text(size = 10, margin = margin(8,0,0,0)),
          panel.grid.major = element_line(colour = "#ebebeb", size = 0.5),
          axis.line = element_blank())

p1
```


Density distributions 

```{r}
df_woody_herb_only$woody_or_herb <- factor(df_woody_herb_only$woody_or_herb,
                                           levels = c("woody", "herb"))

means <- df_woody_herb_only %>% 
    drop_na(resprouting_binomial) %>% 
    group_by(woody_or_herb, resprouting_binomial) %>% 
    summarise(mean = mean(mean_fri))

medians <- df_woody_herb_only %>% 
    drop_na(resprouting_binomial) %>% 
    group_by(woody_or_herb, resprouting_binomial) %>% 
    summarise(median = median(mean_fri))

resprouting_density <-
    df_woody_herb_only %>% 
    drop_na(resprouting_binomial) %>% 
    ggplot(aes(mean_fri, fill = resprouting_binomial)) +
    geom_density(alpha = 0.6, size = 0.8, col = NA) +
    geom_vline(data = means, aes(xintercept = mean, col = resprouting_binomial),
               alpha = 1, size = 1, linetype = "longdash") +
    facet_wrap(~woody_or_herb, ncol = 1, scales = "free") +
    scale_x_log10(expand = c(0,0),
                  limits = c(1.05,5000),
                  breaks = c(10,100,1000),
                  labels = c(10,100,1000)) +
    scale_y_continuous(expand = c(0,0),
                       limits = c(0,1),
                       breaks = c(0,0.5,1.0)) +
    scale_fill_manual(values = c("#EA294C", "#2166AC")) +
    scale_colour_manual(values = c("#EA294C", "#2166AC")) +
    xlab("Fire Return Interval (Yrs)") + 
    ylab("Density") +
    theme_classic() +
    theme(axis.line = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0.5,0.5,0.1,0.1), "cm"),
          panel.border = element_rect(colour = "black", fill = NA),
          panel.spacing = unit(0.5, "lines"),
          axis.text = element_text(colour = "black", size = 8),
          axis.title.y = element_text(size = 10, margin = margin(0,8,0,0)),
          axis.title.x = element_text(size = 10, margin = margin(8,0,0,0)),
          legend.position = "none")
resprouting_density
```



Phylogenetic regression

```{r}
library(phylolm)
library(future)
plan(multisession)

tree <- read.tree("raw_data/v0.1-big-seed-plant-trees/ALLMB.tre")

# Phylogeny tree is available here:
# https://github.com/FePhyFoFum/big_seed_plant_trees
# Smith SA, Brown JW. 2018. Constructing a broadly inclusive seed plant phylogeny. American Journal of Botany 105: 302–314.

df_woody_herb_only$taxon_name <- gsub(" ", "_", df_woody_herb_only$taxon_name)
df_woody_herb_only <- df_woody_herb_only[df_woody_herb_only$taxon_name %in% tree$tip.label,]
df_woody_herb_only$resprouting_binomial <- 
    ifelse(df_woody_herb_only$resprouting_binomial == TRUE, 1, 0) # Make numeric

pruned_tree <- drop.tip(tree, setdiff(tree$tip.label, df_woody_herb_only$taxon_name))
pruned_tree <- as.phylo(pruned_tree)
```


With sorted data (doesn't work otherwise)

```{r}
sorted_data <- df_woody_herb_only[order(match(df_woody_herb_only$taxon_name, pruned_tree$tip.label)),]

sorted_data <-
    sorted_data %>%
    select(taxon_name, mean_fri, resprouting_binomial, woody_or_herb) %>% 
    column_to_rownames("taxon_name")

pglm2 <- phyloglm(resprouting_binomial ~ log10(mean_fri) + I(log10(mean_fri)^2) + log10(mean_fri):woody_or_herb + I(log10(mean_fri)^2):woody_or_herb + woody_or_herb, 
                 method = "logistic_MPLE",
                 data = sorted_data,
                 phy = pruned_tree,
                 btol = 100,
                 boot = 0) 

summary(pglm2)
coef2 <- coef(pglm2)
x1 <- log10(sorted_data$mean_fri)
x2 <- sorted_data$woody_or_herb
x2 <- ifelse(x2 == "woody", 1, 0)
pred_y <- coef2[1] + coef2[2]*x1 + coef2[3]*x1^2 + coef2[4]*x2 + coef2[5]*x1*x2 + coef2[6]*x1^2*x2
pred_p <- exp(pred_y) / (1 + exp(pred_y))
df1 <- data.frame(x1, x2, sorted_data$woody_or_herb, pred_y, pred_p)
df1 <- df1 %>% rename(woody_or_herb = sorted_data.woody_or_herb)

phylo1 <-
    ggplot(data = df1, aes(x = 10^x1, y = pred_p, col = woody_or_herb)) +
    geom_line(size = 1.3) +
    scale_x_log10(breaks = c(10,100,1000),
                  labels = c(10,100,1000)) +
    scale_y_continuous(limits = c(0,1.0),
                       expand = c(0,0)) +
    ylab("Resprouting Probability") +
    xlab("Fire Return Interval (Years)") +
    scale_colour_manual(values = c("#915330", "#aedb65"),
                        name = "", 
                        breaks = c("woody", "herb"),
                        labels = c("Woody", "Herb")) +
    ggtitle("a)") +
    theme_classic() +
    theme(panel.border = element_rect(colour = "black", fill = NA),
          legend.position = "none",
          axis.text = element_text(colour = "black", size = 8),
          plot.margin = unit(c(0.1,0.5,0.1,0.1), "cm"),
          plot.title.position = "plot",
          plot.title = element_text(size = 13, margin = margin(0,0,10,0)),
          axis.title.y = element_text(size = 10, margin = margin(0,8,0,0)),
          axis.title.x = element_text(size = 10, margin = margin(8,0,0,0)),
          panel.grid.major = element_line(colour = "#ebebeb", size = 0.5),
          axis.line = element_blank())
phylo1
```


To calculate R2 Tjur

```{r}
pred <- fitted(pglm2)
y <- pglm2$y

categories <- unique(y)
mean1 <- mean(pred[which(y == categories[1])], na.rm = TRUE)
mean2 <- mean(pred[which(y == categories[2])], na.rm = TRUE)

abs(mean1 - mean2) # 0.013
```



## Seeding binomial


Model without herb data (not enough herbs in dataset)

```{r}
df_woody_only <-
    df_woody_herb_only %>% 
    filter(woody_or_herb == "woody")

m2 <- glm(seeding_binomial ~ log10(mean_fri) + I(log10(mean_fri)^2),
          data = df_woody_only,
          family = binomial)
summary(m2)

ggpredict(m2, c("mean_fri")) %>% 
    ggplot(aes(x, predicted, color = group)) +
    geom_line(size = 1) +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.2, linetype = 0) +
    scale_x_log10() +
    ylab("Seeding Probability") +
    xlab("Mean FRI") +
    theme_classic()

coef2 <- coef(m2)
x1 <- log10(df_woody_only$mean_fri)
x2 <- df_woody_only$woody_or_herb
x2 <- ifelse(x2 == "woody", 1, 0)
pred_y <- coef2[1] + coef2[2]*x1 + coef2[3]*x1^2 
pred_p <- exp(pred_y) / (1 + exp(pred_y))
df1 <- data.frame(x1, x2, df_woody_only$woody_or_herb, pred_y, pred_p)
df1 <- df1 %>% rename(woody_or_herb = df_woody_only.woody_or_herb)

p2 <-
    ggplot(data = df1, aes(x = 10^x1, y = pred_p, col = woody_or_herb)) +
    geom_line(size = 1.3) +
    scale_x_log10(expand = c(0,0),
                  limits = c(1.05,5000),
                  breaks = c(10,100,1000),
                  labels = c(10,100,1000)) +
    scale_y_continuous(limits = c(0,1.0),
                       expand = c(0,0)) +
    ylab("Seeding Probability") +
    xlab("Fire Return Interval (Years)") +
    scale_colour_manual(values = c("#915330"),
                        name = "", 
                        breaks = c("woody"),
                        labels = c("Woody")) +
    ggtitle("b)") +
    theme_classic() +
    theme(panel.border = element_rect(colour = "black", fill = NA),
          legend.position = "none",
          axis.text = element_text(colour = "black", size = 8),
          plot.margin = unit(c(0.1,0.5,0.1,0.1), "cm"),
          plot.title.position = "plot",
          plot.title = element_text(size = 13, margin = margin(0,0,10,0)),
          axis.title.y = element_text(size = 10, margin = margin(0,8,0,0)),
          axis.title.x = element_text(size = 10, margin = margin(8,0,0,0)),
          panel.grid.major = element_line(colour = "#ebebeb", size = 0.5),
          axis.line = element_blank())

p2
```


Density distributions

```{r}
means <- df_woody_herb_only %>% 
    drop_na(seeding_binomial) %>% 
    group_by(woody_or_herb, seeding_binomial) %>% 
    summarise(mean = mean(mean_fri))

medians <- df_woody_herb_only %>% 
    drop_na(seeding_binomial) %>% 
    group_by(woody_or_herb, seeding_binomial) %>% 
    summarise(median = median(mean_fri))

seeding_density <-
    df_woody_herb_only %>% 
    drop_na(seeding_binomial) %>% 
    ggplot(aes(mean_fri, fill = seeding_binomial)) +
    geom_density(alpha = 0.6, size = 0.8, col = NA) +
    geom_vline(data = means, aes(xintercept = mean, col = seeding_binomial),
               alpha = 1, size = 1, linetype = "longdash") +
    facet_wrap(~woody_or_herb, ncol = 1, scales = "free") +
    scale_x_log10(expand = c(0,0),
                  limits = c(1.05,5000),
                  breaks = c(10,100,1000),
                  labels = c(10,100,1000)) +
    scale_y_continuous(expand = c(0,0),
                       limits = c(0,1),
                       breaks = c(0,0.5,1.0)) +
    scale_fill_manual(name = "Resprouting/Seeding",
                      values = c("#EA294C", "#2166AC"),
                      labels = c("No", "Yes")) +
    scale_colour_manual(values = c("#EA294C", "#2166AC")) +
    guides(fill = guide_legend(ncol = 2)) +
    xlab("Fire Return Interval (Yrs)") + 
    ylab("Density") +
    theme_classic() +
    theme(axis.line = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          plot.margin = unit(c(0.5,0.5,0.1,0.1), "cm"),
          panel.border = element_rect(colour = "black", fill = NA),
          panel.spacing = unit(0.5, "lines"),
          axis.text = element_text(colour = "black", size = 8),
          axis.title.y = element_text(size = 10, margin = margin(0,8,0,0)),
          axis.title.x = element_text(size = 10, margin = margin(8,0,0,0)),
          legend.position = "none")

seeding_density
```



Plot resprouting and seeding probability graphs together

```{r}
library(grid)
grid.newpage()
grid.draw(cbind(ggplotGrob(p1), ggplotGrob(p2)))
final_plot <- cbind(ggplotGrob(p1), ggplotGrob(p2))
#ggsave("resprouting_seeding_probabilites.png", plot = final_plot, width = 6, height = 2.8)

cbind(ggplotGrob(resprouting_density), rbind(ggplotGrob(seeding_density1), ggplotGrob(seeding_density2)))

#ggsave("resprouting_densities.png", plot = resprouting_density, width = 3, height = 2.3)
#ggsave("seeding_densities.png", plot = seeding_density, width = 3, height = 2.3)

```



Phylogenetic logistic regression for seeding binomial

```{r}
tree <- read.tree("raw_data/v0.1-big-seed-plant-trees/ALLMB.tre")

# Phylogeny tree is available here:
# https://github.com/FePhyFoFum/big_seed_plant_trees
# Smith SA, Brown JW. 2018. Constructing a broadly inclusive seed plant phylogeny. American Journal of Botany 105: 302–314.

df_woody_herb_only$taxon_name <- gsub(" ", "_", df_woody_herb_only$taxon_name)
df_woody_herb_only <- df_woody_herb_only[df_woody_herb_only$taxon_name %in% tree$tip.label,]
df_woody_herb_only$seeding_binomial <- 
    ifelse(df_woody_herb_only$seeding_binomial == TRUE, 1, 0) # make numeric

pruned_tree <- drop.tip(tree, setdiff(tree$tip.label, df_woody_herb_only$taxon_name))
pruned_tree <- as.phylo(pruned_tree)

sorted_data <- df_woody_herb_only[order(match(df_woody_herb_only$taxon_name, pruned_tree$tip.label)),]

sorted_data <-
    sorted_data %>%
    select(taxon_name, mean_fri, seeding_binomial, woody_or_herb) %>% 
    column_to_rownames("taxon_name") 


pglm1 <- phyloglm(seeding_binomial ~ log10(mean_fri) + I(log10(mean_fri)^2) + log10(mean_fri):woody_or_herb + I(log10(mean_fri)^2):woody_or_herb + woody_or_herb, 
                 method = "logistic_MPLE",
                 data = sorted_data,
                 phy = pruned_tree,
                 btol = 100,
                 boot = 0) 
summary(pglm1)

coef2 <- coef(pglm1)

x1 <- log10(sorted_data$mean_fri)
x2 <- sorted_data$woody_or_herb
x2 <- ifelse(x2 == "woody", 1, 0)
pred_y <- coef2[1] + coef2[2]*x1 + coef2[3]*x1^2 + coef2[4]*x2 + coef2[5]*x1*x2 + coef2[6]*x1^2*x2
pred_p <- exp(pred_y) / (1 + exp(pred_y))
df1 <- data.frame(x1, x2, sorted_data$woody_or_herb, pred_y, pred_p)
df1 <- df1 %>% rename(woody_or_herb = sorted_data.woody_or_herb)


p6 <- 
    ggplot(data = df1, aes(x = 10^x1, y = pred_p, col = woody_or_herb)) +
    geom_line(size = 1.3) +
    scale_x_log10(breaks = c(10,100,1000),
                  labels = c(10,100,1000)) +
    scale_y_continuous(limits = c(0,1.0),
                       expand = c(0,0)) +
    scale_colour_manual(values = c("#B15928", "#B2DF8A"),
                        name = "", 
                        breaks = c("woody", "herb"),
                        labels = c("Woody", "Herb")) +
    ylab("Seeding Probability") +
    xlab("Mean FRI") +
    theme_classic() +
    theme(panel.border = element_rect(colour = "black", fill = NA),
          legend.position = "none",
          axis.text = element_text(colour = "black", size = 9),
          plot.margin = unit(c(0.1,0.5,0.1,0.1), "cm"),
          axis.title.y = element_text(size = 11, margin = margin(0,8,0,0)),
          axis.title.x = element_text(size = 11, margin = margin(8,0,0,0)))
```


Model without herb data

```{r}
df_woody_only <-
    df_woody_herb_only %>% 
    filter(woody_or_herb == "woody")

tree <- read.tree("raw_data/v0.1-big-seed-plant-trees/ALLMB.tre")

# Phylogeny tree is available here:
# https://github.com/FePhyFoFum/big_seed_plant_trees
# Smith SA, Brown JW. 2018. Constructing a broadly inclusive seed plant phylogeny. American Journal of Botany 105: 302–314.

df_woody_only$taxon_name <- gsub(" ", "_", df_woody_only$taxon_name)
df_woody_only <- df_woody_only[df_woody_only$taxon_name %in% tree$tip.label,]
df_woody_only$seeding_binomial <- 
    ifelse(df_woody_only$seeding_binomial == TRUE, 1, 0) # make numeric

pruned_tree <- drop.tip(tree, setdiff(tree$tip.label, df_woody_only$taxon_name))
pruned_tree <- as.phylo(pruned_tree)

sorted_data <- df_woody_only[order(match(df_woody_only$taxon_name, pruned_tree$tip.label)),]

sorted_data <-
    sorted_data %>%
    select(taxon_name, mean_fri, seeding_binomial, woody_or_herb) %>% 
    column_to_rownames("taxon_name")


pglm3 <- phyloglm(seeding_binomial ~ log10(mean_fri) + I(log10(mean_fri)^2), 
                 method = "logistic_MPLE",
                 data = sorted_data,
                 phy = pruned_tree,
                 btol = 100,
                 boot = 0) 
summary(pglm3)

coef2 <- coef(pglm3)

x1 <- log10(sorted_data$mean_fri)
x2 <- sorted_data$woody_or_herb
x2 <- ifelse(x2 == "woody", 1, 0)
pred_y <- coef2[1] + coef2[2]*x1 + coef2[3]*x1^2 
pred_p <- exp(pred_y) / (1 + exp(pred_y))
df1 <- data.frame(x1, x2, sorted_data$woody_or_herb, pred_y, pred_p)
df1 <- df1 %>% rename(woody_or_herb = sorted_data.woody_or_herb)


p5 <-
    ggplot(data = df1, aes(x = 10^x1, y = pred_p, col = woody_or_herb)) +
    geom_line(size = 1.3) +
    scale_x_log10(breaks = c(10,100,1000),
                  labels = c(10,100,1000)) +
    scale_y_continuous(limits = c(0,1.0),
                       expand = c(0,0)) +
    scale_colour_manual(values = c("#915330"),
                        name = "", 
                        breaks = c("woody"),
                        labels = c("Woody")) +
    ggtitle("b)") +
    ylab("Seeding Probability") +
    xlab("Fire Return Interval (Years)") +
    theme_classic() +
    theme(panel.border = element_rect(colour = "black", fill = NA),
          legend.position = "none",
          axis.text = element_text(colour = "black", size = 8),
          plot.margin = unit(c(0.1,0.5,0.1,0.1), "cm"),
          plot.title.position = "plot",
          plot.title = element_text(size = 13, margin = margin(0,0,10,0)),
          axis.title.y = element_text(size = 10, margin = margin(0,8,0,0)),
          axis.title.x = element_text(size = 10, margin = margin(8,0,0,0)),
          panel.grid.major = element_line(colour = "#ebebeb", size = 0.5),
          axis.line = element_blank())
p5

# To calculate odds ratio, exp(estimate)


grid.newpage()
grid.draw(cbind(ggplotGrob(p3), ggplotGrob(p5)))

final_plot <- cbind(ggplotGrob(p3), ggplotGrob(p5))
#ggsave("resprouting_seeding_probabilites_phylo.png", plot = final_plot, width = 6, height = 2.8)
```


To calculate R2 Tjur

```{r}
pred <- fitted(pglm3)
y <- pglm3$y

categories <- unique(y)
mean1 <- mean(pred[which(y == categories[1])], na.rm = TRUE)
mean2 <- mean(pred[which(y == categories[2])], na.rm = TRUE)

abs(mean1 - mean2) # 0.062
```




