---
title: "mean_fri_poisson_regression_method"
author: "Sophie"
date: "22/11/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


Load libraries

```{r}
library(parallel)
library(raster)
library(tidyverse)
library(performance)
```


# Calculate number of fires per pixel


Get list of rasters from MODIS

Win20 = Australia
A list of geoTIFFs for each year and month
See pg 15 of the documentation/user guide for MCD64:
https://lpdaac.usgs.gov/documents/875/MCD64_User_Guide_V6.pdf 

Instructions for obtaining the data begins on pg 22.

```{r}
list_of_files <- 
  list.files("raw_data/MODIS_burn_data_australia/Win20", 
             recursive = TRUE, 
             full.names = TRUE) %>% 
  str_subset("burndate") # Filter for the burndate layers not the QA layers 
```


```{r}
extract_burn_dates <- function(file_path, gbif_coordinates){
    
    # file_path argument must be a string
    raster <- raster(file_path)
    
    # Extract year from file_path
    year <- str_match(file_path, "(?<=.A)[0-9]{4}")
    
    # Extract intersecting pixels
    intersecting_pixels <- raster %>% 
        raster::extract(gbif_coordinates, sp = TRUE)
    
    # Convert to data frame
    df <- 
        intersecting_pixels %>% 
        raster::as.data.frame() %>% 
        rename(burn_date = contains("burndate")) %>% 
        select(decimalLongitude, decimalLatitude, burn_date) %>% 
        # Filter out -2 and 0 values
        filter(burn_date > 0) %>% 
        # Convert Julian date to calendar date
        mutate(burn_date = as.Date(burn_date - 1, origin = str_glue("{year}-01-01"))) 
    
    return(df)
}
```


Apply function to extract burn dates

```{r}
burn_dates_df <- map_dfr(list_of_files, extract_burn_dates) 
burn_dates_df <- burn_dates_df %>% arrange(x, y, burn_date)
```


Use group_by and summarise to count the number of burns per pixel

```{r}
num_of_fires_df <-
    burn_dates_df %>% 
    group_by(x, y) %>% 
    summarise(num_of_fires = sum(burn_date != 0)) %>% 
    ungroup()
```



```{r}
init_raster <- raster("raw_data/Win20/2000/MCD64monthly.A2000306.Win20.006.burndate.tif") 
# Resolution = 0.004
# Extent: 112, 155.0005, 0.004394531, -10 (xmin, xmax, ymin, ymax)

init_df <- init_raster %>% as.data.frame(xy = TRUE)
init_df <- 
    init_df %>% 
    rename(burn_date = contains("burndate")) %>% 
    filter(burn_date >= 0) %>% 
    arrange(x, y) %>% 
    select(x, y) 
full_fires_df <- full_join(init_df, num_of_fires_df, by = c("x", "y"))

nrow(full_fires_df)
nrow(init_df)
nrow(num_of_fires_df)
# 18.6% of pixels burned (but this includes water pixels)

full_fires_df <- full_fires_df %>% replace_na(list(num_of_fires = 0))

# Filter out values outside of Australia
full_fires_no_water <- 
    full_fires_df %>% 
    filter(x > 143 | y > -39) %>% 
    filter(x > 120 | y > -36) %>% 
    filter(x > 126 | y < -12) %>% 
    filter(x < 145 | y < -14)

#saveRDS(full_fires_no_water, file = "processed_data/num_of_fires_df.rds")
#full_fires_no_water <- readRDS("processed_data/num_of_fires_df.rds")

num_fires_raster <- rasterFromXYZ(full_fires_no_water)

plot(num_fires_raster)

writeRaster(num_fires_raster, "processed_data/num_fires_map", format = "GTiff", overwrite = TRUE)
```


Read in number of fires raster and gbif data

```{r}
num_of_fires <- raster("processed_data/num_fires_map.tif")

# Read in fire response and gbif data
fire_response_and_gbif_data <- readRDS(file = "processed_data/fire_response_and_gbif_data.rds")
# Produced from "code/extracting_fire_response_data.Rmd"
```



Safely and quietly function combined to catch errors, warnings and messages
https://github.com/tidyverse/purrr/issues/426

```{r}
safely_n_quietly <- function(.f, otherwise = NULL) {
    retfun <- quietly(safely(.f, otherwise = otherwise, quiet = FALSE))
    function(...) {
    ret <- retfun(...)
    list(result = ret$result$result,
         output = ret$output,
         messages = ret$messages,
         warnings = ret$warnings,
         error = ret$result$error)
  }
}
```


Function that returns a data frame with predicted FRI and other metrics

```{r}
calculate_mean_fri_with_glm <- function(taxon, gbif_data = fire_response_and_gbif_data, num_of_fires_raster = num_of_fires, sampling_period = 20.66){
    
    # Subset data to taxon
    species_subset <-
        gbif_data %>% 
        filter(taxon_name == taxon) %>% 
        select(decimalLongitude, decimalLatitude)
    
    # Round species_subset to resolution of 0.005 decimal degrees so that any coordinates
    # that are approximately within the same MODIS pixel can be removed
    multiple <- 0.005
    species_subset <-
        species_subset %>% 
        mutate(decimalLongitude = multiple*round(decimalLongitude/multiple),
               decimalLatitude = multiple*round(decimalLatitude/multiple)) %>% 
        distinct(.keep_all = TRUE) # Remove duplicates
    
    # Convert to a SpatialPointsDataFrame
    spdf <- SpatialPointsDataFrame(coords = species_subset,
                                   data = species_subset, 
                                   proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs"))
 
    # Extract intersecting pixels
    intersecting_pixels <- 
        num_of_fires_raster %>% 
        raster::extract(spdf, sp = TRUE) 
    
    # Convert to data frame
    df <-
        intersecting_pixels %>% 
        raster::as.data.frame() %>% 
        rename(num_of_fires = num_fires_map) %>% 
        select(decimalLongitude, decimalLatitude, num_of_fires) %>% 
        filter(!is.na(num_of_fires)) # Filter out NAs
    
    # Run GLM model
    safe_quiet_glm <- safely_n_quietly(glm)
    model <- safe_quiet_glm(num_of_fires ~ 1, data = df, family = poisson(link = "identity"))
    
    
    if(length(model$error) < 1) {
        
        # Get summary
        summary <- summary(model$result)
        
        # Calculate mean number of fires in 20 years
        mean_fires_in_sampling_period <- model$result$coefficients[[1]]
        
        # Calculate predicted fire return interval
        predicted_fri <- sampling_period / predict(model$result, type = "link")[[1]]
        
        # Lower confidence interval bound
        lwr <- 
            sampling_period / 
            (predict(model$result, type = "link")[[1]] + summary$coefficients[[2]]*1.96)
    
        # Upper confidence interval bound
        upr <- 
            sampling_period / 
            (predict(model$result, type = "link")[[1]] - summary$coefficients[[2]]*1.96)

        # Dispersion test
            dispersion_test <- check_overdispersion(model$result)
        
        # Return outputs 
        output_df <- data.frame(taxon_name = taxon,
                                mean_fires = mean_fires_in_sampling_period,
                                mean_fri = predicted_fri,
                                lwr_confint = lwr,
                                upr_confint = upr,
                                dispersion_ratio = dispersion_test$dispersion_ratio,
                                dispersion_p_value = dispersion_test$p_value,
                                num_unburnt_pixels = df %>% 
                                    filter(num_of_fires == 0) %>% 
                                    nrow(),
                                num_pixels = nrow(df),
                                warnings = ifelse(length(model$warnings) >= 1, 
                                                  paste(model$warnings, 
                                                        collapse = ", "), NA),
                                messages = ifelse(length(model$messages) >= 1, 
                                                  paste(model$messages, 
                                                        collapse = ", "), NA),
                                error = NA)
            
    } else {
        
        # Return outputs 
        output_df <- data.frame(taxon_name = taxon,
                                mean_fires = NA,
                                mean_fri = NA,
                                lwr_confint = NA,
                                upr_confint = NA,
                                dispersion_ratio = NA,
                                dispersion_p_value = NA,
                                num_unburnt_pixels = df %>% 
                                    filter(num_of_fires == 0) %>% 
                                    nrow(),
                                num_pixels = nrow(df),
                                warnings = ifelse(length(model$warnings) >= 1, 
                                                  paste(model$warnings, 
                                                        collapse = ", "), NA),
                                messages = ifelse(length(model$messages) >= 1, 
                                                  paste(model$messages, 
                                                        collapse = ", "), NA),
                                error = paste(model$error, collapse = ", "))
    }
    
    return(output_df)
    
}
```



Extract list of unique taxa 

```{r}
list_of_taxa <- fire_response_and_gbif_data$taxon_name %>% unique()
```


Find number of cores

```{r}
num_cores <- detectCores()
```


Calculate mean FRI in parallel

```{r}
mean_fri_list <- 
    mclapply(list_of_taxa, 
             calculate_mean_fri_with_glm, 
             mc.cores = num_cores)
```



Bind into data frame

```{r}
mean_fri_df <- mean_fri_list %>% bind_rows()
```


Write to a csv file

```{r}
write_csv(mean_fri_df, "processed_data/mean_fris_from_poisson_method.csv")
```


---

Out of 8009 taxa, 294 did not fit and they were all because all pixels were unburnt.
Out of the 7715 with no errors, 419 had confidence intervals bounding zero, which 
were discarded, leaving us with 7296 taxa. There were 2 taxa with mean FRI greater
than 5000 years. 5574 taxa had confidence intervals less than 100 years big. 

```{r}
mean_fris <- read_csv("processed_data/mean_fris_from_poisson_method.csv", guess_max = 8009)

mean_fris %>% filter(mean_fri > 1000) %>% nrow()
mean_fris_clean %>% filter(upr_confint - lwr_confint < 100) %>% nrow()

mean_fris_clean %>% mutate(confint_size = upr_confint - lwr_confint) -> y
hist(y$confint_size)
```



Comparatively, the survival analysis resulted in 1443 that did not fit (incl. unburnt
pixels). The warning was "ran out of iterations and did not converge". This occurred 
because most or all pixels were unburnt. There were 7217 taxa with median FRI greater
than 5000 years. 221 taxa had confidence intervals less than 100 years big. 

```{r}
median_fris <- read_csv("processed_data/median_fris_from_survival_method.csv", guess_max = 8009)
median_fris <- 
    median_fris %>% 
    mutate(across(c("med_w", "med_w_lwr", "med_w_upr", "med_wo", "med_wo_lwr", "med_wo_upr"),
                  ~ .x / 365.2422))

median_fris %>% filter(med_w > 1000) %>% nrow()
median_fris %>% filter(med_w_upr - med_w_lwr < 100) %>% nrow()
median_fris %>% mutate(confint_size = med_w_upr - med_w_lwr) -> x
hist(x$confint_size)

median_fris %>% filter(!is.na(med_wo_warnings)) %>% nrow()
median_fris %>% filter(med_wo > 5000) %>% nrow()


```

1282 that did not fit (when not including unburnt pixels). There were 6719 taxa with
median FRI greater than 5000 years. 

